Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added retro positive diagnosis by sample graphs, with and without angled x axis text

@@

dat.retro_positive_diagnosis_by_sample %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Retro Diagnoses of the GLAD/EDGI, NBR and RAMP cohorts",
       x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

>>>>

###Retro
####Style 1

@@

dat.retro_positive_diagnosis_by_sample %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Retro Diagnoses of the GLAD/EDGI, NBR and RAMP cohorts",
       x = "",
       y = "") +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(legend.position = "top") + 
  theme(legend.title = element_blank())

@@

####Style 2

dat.retro_positive_diagnosis_by_sample %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Retro Diagnoses of the GLAD/EDGI, NBR and RAMP cohorts",
       x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "top") + 
  theme(legend.title = element_blank())
